Mathematical Gene Network Evolution

### 2017-01-30 kalman_walk.tex
biblio stuff.
notes

\documentclass[11 pt]{article}
\usepackage{amsmath, amssymb, color, xcolor}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{caption, subcaption}

@@

%$\unobservable$

@@

% is y the phenotype or H(z) the phenotype? Do we need new jargon anyway? 
% 
\title{Mathematical Gene Network Evolution}
\maketitle

@@

\begin{tikzpicture}
\begin{scope}[every node/.style={circle,thick,draw}]
  \node (A) at (0,0) {$x_{1}$};
    \node[dashed] (B) at (3,0) {$x_{2}$};
    \node[shape=rectangle, dashed] (U) at (1.5,-2) {$u(t)$};
\end{scope}

\begin{scope}[>={Stealth[black]},
              every node/.style={fill=white,circle},
              every edge/.style={draw=black, thick}]
    \path [->, >=Rectangle] (A) edge[bend left] node {\tiny $-1$} (B);
    \path [->] (B) edge[bend left] node {\tiny $1$} (A); 
    \path[->] (U) edge[dashed] node {\tiny $1$} (A);
    \path[->] (U) edge[dashed] node {\tiny $1$} (B);
\end{scope}
\begin{scope}[>={Stealth[black]},
              every edge/.style={draw=black, thick}]
    %\path [->] (A) edge[loop left] node {\tiny $\lambda_{1}$} (A);
    %\path [->] (B) edge[loop left] node {\tiny $\lambda_{2}$} (B);
\end{scope}

\end{tikzpicture}

@@

>>>>

\documentclass[11 pt]{article}
\usepackage{amsmath, amssymb, color, xcolor}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, shapes}
\usepackage{caption, subcaption}
\usepackage{natbib} % gives us \citet: Author (year) and \citep: (Author; year)

@@

\paragraph{To do, soon:}

\begin{enumerate}
    \item Add biology to introduction. (keep an eye out for concrete numbers we can use!)

    \item Do some order-of-magnitude calculation to figure out how fast systems should drift.

    \item Write out simple examples in biological words.

    \item Rephrase hybrid inviability example in biological terms.  Discuss F1's (or heterozygotes) versus F2's.

    \item Clarify our assumptions around $x(0)$.

    \item Note we don't include $D$ for simplicity but don't.

    \item Figure out how to specify $P$ for Kalman decomposition.

    \item Prove or find citation for uniqueness of minimal system up to basis change.

    \item Work examples (minimal; not minimal; with/without B,C fixed) of Kalman decomposition and description of moving along the walk.

    \item Write down and decide between options for parameterizing the random walk on the neutral manifold:
        use Kalman decomposition, and parameterize Brownian motion so that it has constant speed;
        OR consider Josh's parameteriziation like this;
        OR just say we do Brownian motion on the manifold (more or less implicit characterization).

    \item Consider options for fitness function: Euclidean? Sign of eigenvalues?  Time domain or frequency?
        First try on simple concrete examples.

    \item Describe model leading to constraints on regulation so we have a stationary distribution.
        Ask questions of stationary distribution: robustness, connectivity, xxx?

    \item Write something in discussion about nonlinear systems.  Do an example if there is a feasible one.

\end{enumerate}

@@

%%% Questions:

% is y the phenotype or H(z) the phenotype? Do we need new jargon anyway?

\title{Mathematical Gene Network Evolution}
\maketitle

@@

    \begin{figure}
        \begin{center}
            \begin{tikzpicture}
            \begin{scope}[every node/.style={circle,thick,draw}]
                \node (A) at (0,0) {$x_{1}$};
                \node[dashed] (B) at (3,0) {$x_{2}$};
                \node[shape=rectangle] (U) at (1.5,2) {$u$};
                \node[shape=rectangle] (y) at (1.5,-2) {$y$};
            \end{scope}

            \begin{scope}[>={Stealth[black]},
                          every node/.style={fill=white,circle},
                          every edge/.style={draw=black, thick}]
                \path [->, >=Rectangle] (A) edge[bend left] node {\tiny $-1$} (B);
                \path [->] (B) edge[bend left] node {\tiny $1$} (A); 
                \path[->] (U) edge[dashed] node {\tiny $1$} (A);
                \path[->] (U) edge[dashed] node {\tiny $1$} (B);
                \path[->] (A) edge[dashed,bend right] node {\tiny $1$} (y);
            \end{scope}
            \begin{scope}[>={Stealth[black]},
                          every edge/.style={draw=black, thick}]
                %\path [->] (A) edge[loop left] node {\tiny $\lambda_{1}$} (A);
                %\path [->] (B) edge[loop left] node {\tiny $\lambda_{2}$} (B);
            \end{scope}

            \end{tikzpicture}
        \end{center}
        \caption{
            Diagram of Example \ref{ex:osc} in the text.  
            \plr{explain what arrows mean if nec}
            \label{fig:oscillator_diagram}}
    \end{figure}

@@

Distribution of dominance coefficients.

\bibliographystyle{plainnat}
\bibliography{krefs}
